---
title: "Text Analysis - Car Reviews"
author: "Deepanshu Goyal"
date: "December 10, 2019"
output:
  html_document: default
  word_document: default
---


```{r Install required package & custom functions, warning=FALSE}

rm(list=ls()) 
source('https://raw.githubusercontent.com/deepanshu-goyal/Text-Analytics/master/Common_Functions.R')

```

## Read car reviews
Read Kia Seltos, Jeep Compass & MG Hector car reviews scrapped from cardekho.com, carwale.com & team-bhp.com

```{r Car Reviews}
setwd(getwd())
data = read.csv('https://raw.githubusercontent.com/deepanshu-goyal/Text-Analytics/master/FinalReview.csv', header = TRUE,sep = ',')

seltos = data %>% filter(Brand=='Kia Seltos')
Compass = data %>% filter(Brand=='Jeep Compass')
hector = data %>% filter(Brand=='MG Hector')

```

## Random sample same number of reviews for each car type 

Random sample 175 reviews for each car, this will help in comparative analysis.We have used sample without replacement to get one review only once. 

```{r sampling}
seltos_sample = sample_n(seltos, 175, replace = FALSE)
compass_sample = sample_n(Compass, 175, replace = FALSE)
hector_sample = sample_n(hector, 175, replace = FALSE)

```

## Text Analytics 1: Count frequency of different ratings

```{r Frequency of ratings, echo=FALSE}
seltos_rating_freq = seltos_sample %>% count(Rating) %>% rename(seltos_count=n)
print(seltos_rating_freq)

compass_rating_freq = compass_sample %>% count(Rating) %>% rename(compass_count=n)
print(compass_rating_freq)

hector_rating_freq = hector_sample %>% count(Rating) %>% rename(hector_count=n)
print(hector_rating_freq)
```

## Text Analytics 2: create DTM

```{r}
seltos_dtm = create_dtm(seltos);seltos_dtm[1:8,1:8]
compass_dtm = create_dtm(Compass);compass_dtm[1:8,1:8]
hector_dtm = create_dtm(hector);hector_dtm[1:8,1:8]

```


## Text Analytics 3: Simple bar chart of top tokens

```{r}
token1 = word_tokens(seltos)
token2 = word_tokens(Compass)
token3 = word_tokens(hector)
#Bar chart for Kia Seltos
bar_chart(token1,'Top 20 words for Kia Seltos')
#Bar chart for Jeep Compass
bar_chart(token2,'Top 20 words for Jeep Compass')
#Bar chart for MG Hector
bar_chart(token3,'Top 20 words for MG Hector')

common_token =  intersect(token1$word,token2$word) %>% intersect(token3$word)

print(common_token)
```

## Text Analytics 4: Wordcloud of top tokens
```{r}
wordcloud(token1$word,token1$n,scale = c(2, 0.5),colors = brewer.pal(8, "Dark2"))
wordcloud(token2$word,token2$n,scale = c(2, 0.5),colors = brewer.pal(8, "Dark2"))
wordcloud(token3$word,token3$n,scale = c(2, 0.5),colors = brewer.pal(8, "Dark2"))
```

# Text Analytics 5: Create Bigrams 

```{r}
#Bigrams for Seltos
seltos_bigram = create_bigram(seltos) %>% top_n(20)
print(seltos_bigram)
#Bigrams for Compass
compass_bigram = create_bigram(Compass) %>% top_n(20)
print(compass_bigram)
#Bigrams for Hector
hector_bigram = create_bigram(hector) %>% top_n(20)
print(hector_bigram)
```
## Text Analytics 6: Create Co-occurance graphs i.e. two words occured most of the time within a document. 

```{r}
distill.cog(seltos_dtm,'Kia Seltos COG',15)
distill.cog(compass_dtm,'Jeep Compass COG',15)
distill.cog(hector_dtm,'MG Hector COG',15)
```